Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/paper.tex
pass on results

%Figure~\ref{fig:summary} summarizes the bugs we reported.

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figures~\ref{fig:stacked-engine}
and~\ref{fig:stacked-technique} show bugs reports per engine and
technique, respectively. Each stacked bar breaks down the bugs per
status. Note that several of these bugs were already fixed and
incorporated in the latest release of the corresponding
engines. Overall, discarding bug report with the ``new'' status, we
reported a total of \noBugsTotalConfirmed{} bugs. Considering the
engines, the majority of bug reports targeted \chakra\ and
\jsc. Considering the techniques, the number of bug reports issued
and confirmed were similar. We found, however, that the cost of
inspecting \Fix{...elaborate...}

%% It is
%% also worth noting that several of these reports hold the status
%% ``new'', which indicates that they were not reviewed yet by the
%% development team. Note also that we did not find bugs in the Mozilla
%% \smonkey\ engine.

\begin{figure}[t!]
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}        
  }
  \caption{\label{fig:summary}Summary of bug reports.}
\end{figure}

@@

\begin{wraptable}[12]{r}{0.25\textwidth}
  \vspace{-3ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
\end{wraptable}

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

\begin{table}[t!]
\setlength{\tabcolsep}{5pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{rcccccc}
    \toprule Issue\#\Comment{    & Date} & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  \Comment{& 4/18  }& JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  \Comment{& 4/23 }& \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\

   3  \Comment{& 4/29 }& \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}}
    & 2 & \smonkey{} \\

    \multirow{2}{*}{4}\Comment{& \multirow{2}{*}{4/29}} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &\Comment{  &}
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   5 \Comment{& 5/02  }& \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 \Comment{& 5/17  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 \Comment{& 5/21  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 \Comment{& 6/28  }& \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 \Comment{& 7/10  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 \Comment{& 7/18  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
   13 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   14 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   15 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   16 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   17 \Comment{& 8/08  }& \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   18 \Comment{& 8/08  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   19 \Comment{& 8/16  }& \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
   20 \Comment{& 8/22  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
   21 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
   22 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{?????????????????????}{???}} & - & \smonkey{}\\
%   \midrule
    \multirow{3}{*}{23}\Comment{& 
    \multirow{3}{*}{8/22}} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
    &  \Comment{&}
    \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
    &  \Comment{&}
    \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
%   \midrule
   24 \Comment{& 8/23  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
%    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & \lo{} & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & \hi{} & \jsc{} \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & \hi{} & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & \hi{} & \jerry{}   \\
    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & \hi{}  & \jerry{}\\
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & \lo{} & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & \hi{} & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & \hi{} & \veight{}\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & \hi{} & \jsc{}\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & \hi{} & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & \hi{} & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & \hi{} & \jerry{}\\
%    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
    \multirow{2}{*}{radamsa} & \chakra{} & New &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & &
    \veight{} & \textbf{Confirmed} &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
    & - &  & \\
    15 & 8/23 & quickfuzz & \jsc{} & New  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
    & - & \hi{} & Test262\\
    16 & 8/23 & quickfuzz & \veight{} & New  &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
    & - & \hi{} & Test262\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows a
summary of the bugs we reported. The figure shows the distribution of
status of bug reports per engine. Note that several of these reports
hold the status ``new'', which indicates that they were not reviewed
yet by the development team. Note also that we did not find bugs in
the Mozilla \smonkey\ engine and that several of the bugs we reported
were already fixed and incorporated in the latest release of
corresponding engines. Overall, discarding bug report with the ``new''
label, we reported \noBugsTotalConfirmed{} bugs.

\begin{figure}[h]
  \centering
  \includegraphics[trim=0 120 0 150,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked}  
  \caption{\label{fig:summary}Summary of bug reports per engine and status.}
\end{figure}

@@

\begin{wraptable}[12]{r}{0.25\textwidth}  
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.\Mar{Please, use percentages.}}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\
    \smonkey{} & 93\% \\
    \bottomrule 
  \end{tabular}
  \normalsize
\end{wraptable}

%% It is important to note that failures are
%% expected as it takes time for engines to adjust to the
%% spec.

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in Test262 (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not expect causality. We
conjecture that the development age of the engine--Chakra is the
newest engine\Fix{find DOB of Chakra}--justify the incidental
correlation.

%% The rationale is that lack of support
%% to features (as measured by conformance testing) and reliability of
%% engines (as measured in this study) may have some relationship.

@@

\input{table_transplantation}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
%    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & \lo{} & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & \hi{} & \jsc{} \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & \hi{} & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & \hi{} & \jerry{}   \\
    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & \hi{}  & \jerry{}\\
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & \lo{} & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & \hi{} & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & \hi{} & \veight{}\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & \hi{} & \jsc{}\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & \hi{} & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & \hi{} & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & \hi{} & \jerry{}\\
%    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & &
    \veight{} & \textbf{Confirmed} &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
    & 2 &  & \\
    15 & 8/23 & quickfuzz & \jsc{} & New  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
    & - & \hi{} & Test262\\
    16 & 8/23 & quickfuzz & \veight{} & New  &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
    & - & \hi{} & Test262\\
    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & &
    \jsc{} & New &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
    & - &  & \\
   \bottomrule
  \end{tabular}
\end{table*}
